\begin{cvsection}{Work Experience}
	\begin{cvsubsection}{Software Engineer, Intern}{Apple Computer}{Summer 2004}
		iChat AV			
		\begin{itemize}
			\item Reduced time to render the user’s buddy list by 75\% by implementing prediction algorithm.
			\item Implemented iChat integration with OS X Spotlight Search by creating tool which extracts metadata from saved chat transcripts and provides metadata to a system-wide search database.
			\item Redesigned chat file format and implemented backwards compatibility for search.
		\end{itemize}
	\end{cvsubsection}
	
	\begin{cvsubsection}{Lead Student Ambassador}{Microsoft Corporation}{Fall 2003 -- Spring 2005}	
		\begin{itemize}
			\item Promoted to Lead Student Ambassador in Fall 2004; supervised 10 -- 15 Student Ambassadors.
			\item Created and taught Computer Science course, CSE 099: Software Design and Development.
		\end{itemize}
	\end{cvsubsection}
	
	\begin{cvsubsection}{Head Teaching Assistant}{University of Pennsylvania}{Fall 2001 -- Spring 2005}		
		\begin{itemize}
			\item Courses: Advanced Java III, Software Engineering, Mathematical Foundations of Computer Science I \& II.
			\item Promoted to Head TA in Fall 2004; led weekly meetings and supervised four other TAs.
		\end{itemize}
	\end{cvsubsection}
	
	\begin{cvsubsection}{Software Design Engineer, Intern}{Microsoft Corporation}{Summers 2001 -- 2003}
		Visual Studio Core (Summer 2003)		
		\begin{itemize}
			\item Implemented a user interface for the VS open file switcher (ctrl-tab) and extended it to tool windows.
			\item Created service to provide gradient across VS and VS add-ins. Optimized service via caching.
		\end{itemize}
		Programmer Productivity Research Center (Summers 2001, 2002)
		\begin{itemize}
			\item Built app to compute similarity of all methods in a code base; reduced time from $O(n^2)$ to $O(n\ log\ n)$. 
			\item Created test case generation tool which creates random XML docs from XML Schema.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}