%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{lau}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Anthony Lau}
\title{Software Developer}
\contacts{(512)913-1251\linebreak anthonycylau@gmail.com\linebreak anthonylau.dev}

\begin{document}

	% Print the header
	\makeheader

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{StateFarm}{5/2018 – Present, Richardson TX}
			PL \& BL Modernization Devops
			\begin{itemize}
				\item Reduced of staging time by factor of days by redesigning of business rules storage application (\textbf{React.js, Spring Boot, MongoDB})
				\item Deployed and maintained Gitlab pipelines (\textbf{Gitlab runners, Docker, Vault integrations, Kubernetes integrations})
				\item Implemented \textbf{Prometheus} and \textbf{Grafana} dashboard for effort wide telemetry. Helped identify key bottlenecks in administrative process.
				\item Developed and maintained data fabrication tools in \textbf{Node.js} for auto policies.
				\item Migrated services from IaaS platforms to internal \textbf{Kubernetes} CaaS platform.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Devloper, Intern}{StateFarm}{8/2017 - 12/2017, Richardson TX}
			Automation Center of Excellence (Fall 2017)
			\begin{itemize}
				\item Automated server changes with \textbf{Perl} scripts. Reducing server maintenance time.
				\item Designed UI (\textbf{HTML, CSS}) changes to the internal WiFi connection site.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Devloper, Intern}{StateFarm}{5/2017- 8/2017, Richardson TX}
			PolicyCenter (Fall 2017)
			\begin{itemize}
				\item Developed tests using \textbf{BDD} framework with \textbf{Selenium} web driver.
				\item Created \textbf{Jenkins} jobs for running hundreds of UI tests concurrently.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Volunteer Experience}
		\begin{cvsubsection}{Apollo Coding Club}{StateFarm}{2019-Present, Richardson TX}
			\begin{itemize}
				\item Served as a volunteer to introduce girls in middle school Scratch Studio JavaScript
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Dallas, TX}{University of Texas at Dallas}{2014-2018}
			\begin{itemize}
				\item B.S. in Computer Science, May 2018. GPA: 3.7
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Cat and lilies (catandlilies.onrender.com)} (2021). One of my favorite board games digitized. Personal project for learning how to use WebSockets and \textbf{Vue.js}. Built with \textbf{Vue.js}, \textbf{Express.js}, and \textbf{Socket.io}. Assets created with \textbf{Inkscape}.
				\item \textbf{CometThon} (2017). Created school club website for new members to learn about CometThon as well as membership sign up forms. (\textbf{CSS, HTML})
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Certifications}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{AWS Certified Cloud Practitioner} 6/2020
				\item \textbf{Certified Kubernetes Application Developer (CKAD)} 8/2019
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item JavaScript(Node.js), Java, Python, Bash / Zsh, HTML, CSS, Perl
				\item Kubernetes, Docker, AWS, Azure
				\item Gitlab CI/CD, Jenkins, Travis CI
				\item Vim, Git/SVN, Prometheus, Grafana, Agile/Scrum, Selenium, Inkscape, Vault
				\item Express, React.js, Vue.js, Spring Boot, PostgreSQL, MongoDB
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

\end{document}
